Market-based Mechanisms for Resource Scheduling

### 2013-12-18 paper/paper.tex

Large-scale computing clusters offer the potential for greater efficiency through
pooling of computational resources, but must contend with the problem of
allocating these resources to users with competitive and potentially
incompatible demands. Such conflicts are typically arbitrated by some \emph{fairness}
criteria, such as dominant resource fairness (DRF) \cite{drf}, which benefit from their
simplicity, efficiency, and non-manipulability. Unfortunately, when applied in
realistic settings --- when dealing with inhomogeneous resources, time-varying
demands or deadlines, requirements for data locality, etc.---typical implementations
of these systems cease to be either
efficient or non-manipulable.

@@

\subsection{Ascending-bid clock auction}
Once the master has collected a set of bids, it uses an ascending-bid clock
auction to determine which of the bids to fulfill, and how much it should charge
for each of the tasks which win the auction. The auction consists of a number of
rounds which continue until no changes occur in the final round. To avoid the
need for communication between the master and the frameworks after each round,
we use a \emph{proxy auction} where each framework makes a single bid for all
rounds and agents running with the master represent each of them within the
master.

@@

\subsection{Grid computing}
Job schedulers like TORQUE \cite{torque}, Condor \cite{condor}, and LSF
\cite{lsf} have long been used for solving the problem of resource allocation
within a high-performance-computing (HPC) or grid-computing environment.
For the most part, they do not use a two-level scheduling model like we do but
instead operate as a queue for predefined jobs which are run as resources become
available. Machines and job requirements also tend to show more homogeneity
within such environments (for example, the ratio between CPU, memory, and disk),
so the amount of optimization possible with pricing is lower.

>>>>

Large-scale computing clusters offer the potential for greater efficiency through
pooling of computational resources, but must contend with the problem of
allocating these resources to users with competitive and potentially
incompatible demands. Such conflicts are typically arbitrated by some \emph{fairness}
criterion, such as dominant resource fairness (DRF) \cite{drf}, which benefit from their
simplicity, efficiency, and non-manipulability. Unfortunately, when applied in
realistic settings --- when dealing with inhomogeneous resources, time-varying
demands or deadlines, requirements for data locality, etc.---typical implementations
of these systems cease to be either
efficient or non-manipulable.

@@

\subsection{Ascending-bid clock auction}
Once the master has collected a set of bids, it uses an ascending-bid clock
auction to determine which of the bids to fulfil, and how much it should charge
for each of the tasks which win the auction. The auction consists of a number of
rounds which continue until no changes occur in the final round. To avoid the
need for communication between the master and the frameworks after each round,
we use a \emph{proxy auction} where each framework makes a single bid for all
rounds and agents running with the master represent each of them within the
master.

@@

\subsection{Grid computing}
Job schedulers like TORQUE \cite{torque} or Condor \cite{condor} have long been used for solving the problem of resource allocation
within a high-performance-computing (HPC) or grid-computing environment.
For the most part, they do not use a two-level scheduling model like we do but
instead operate as a queue for predefined jobs which are run as resources become
available. Machines and job requirements also tend to show more homogeneity
within such environments (for example, the ratio between CPU, memory, and disk),
so the amount of optimization possible with pricing is lower.
